\documentclass[journal,12pt,twocolumn]{IEEEtran}
\usepackage{kvmap}
\usepackage{hyperref}
\usepackage{xcolor}
%\usepackage{lipsum}
%\usepackage[htt]{hypenat}

\definecolor{bgcolor}{gray}{0.95}
\let\oldtexttt\texttt
\renewcommand{\texttt}[1]{%
	\colorbox{bgcolor}{\oldtexttt{#1}}}
%\let\oldurl\url
%\renewcommand{\url}{%
%	\colorbox{bgcolor}{\oldurl{#1}}}

\title{XNOR Gate in Arduino}
\author{Ahilan R - FWC22090}

\begin{document}
\maketitle
\bigskip
\begin{abstract}
We implement XNOR logic in Arduino by getting the boolean expression from it's K-map for it's truth table. 
\end{abstract}

\section{\textbf{Theory}}
Let $A$ and $B$ be the inputs to the gate, $Y$ be the output. The truth table for XNOR gate is given below.

%\subsection{Truth Table}
\begin{table}[h]
	\centering
	\begin{tabular}[20pt]{|c|c|c|}
		\hline
		\textbf{A}&\textbf{B}&\textbf{Y}\\
		\hline
		0&0&1\\
		\hline
		0&1&0\\
		\hline
		1&0&0\\
		\hline
		1&1&1\\   
		\hline 
	\end{tabular}
\end{table}

%\subsection{K-map}
K-map for the above mentioned truth table:\\
\begin{table}[h]
	\centering
	\begin{kvmap}
		\kvlist{2}{2}{1,0,0,1}{B,A}
	\end{kvmap}
\end{table}

Simplified K-map:
\begin{table}[h]
	\centering
	\begin{kvmap}
		\kvlist{2}{2}{1,0,0,1}{B,A}
		\bundle[color=red,reducespace=1pt]{0}{0}{0}{0}
		\bundle[color=red,reducespace=1pt]{1}{1}{1}{1}
		\bundle[color=green,reducespace=1pt]{1}{0}{1}{0}
		\bundle[color=green,reducespace=1pt]{0}{1}{0}{1}
	\end{kvmap}
\end{table}

%\subsection{Boolean Expression}
Collecting minterms from the kmap, i.e., where $Y=1$, we get the boolean expression in sum of products form for XNOR gate as following.
\begin{equation}
	Y = A^{\prime}B^{\prime}  +  AB
\end{equation}
And for product of sums form, we get maxterms, where $Y=0$, we get the boolean expression as following.
\begin{equation}
	Y = (A^{\prime}+B)(A+B^{\prime})
\end{equation}
\newpage

\section{\textbf{Implementation}}
\bigskip

%\subsection{Components required}
Components Required:
\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\textbf{Components}&\textbf{Qty.}\\
		\hline
		Arduino UNO&1\\
		\hline
		Breadboard&1\\
		\hline
		Jumper wires&4\\
		\hline
	\end{tabular}
\end{table}

%\subsection{Connections}
Connections:
\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		\textbf{Arduino}&2&3\\
		\hline
		\textbf{Inputs}&A&B\\
		\hline
	\end{tabular}
\end{table}

In addition to the above table, we connect $5V$ and $GND$ pins of Arduino to different bus strips of breadboard to input binary values back to the input pins of Arduino.

\subsection{Sketch}
We set the digital pins D2, D3 as inputs and feed A, B into those. We utilise the builtin LED at D13, by setting D13 as output. So, when $Y=1$, LED glows and when $Y=0$ LED doesn't glow. This sketch is given in the below link.

\bigskip

\url{https://github.com/ahilan22/fwc-1/tree/main/ide/assignment/code/src/main.cpp}

\subsection{Software}
We use platformIO to compile and upload the code to Arduino. 
\bigskip
%\texttt{\lipsum[1]}
\begin{enumerate}
	\item Download the source code%; from a desired directory run the command
		\begin{itemize}
			\item \texttt{svn export https://github}
				\\ \texttt{.com/ahilan22/fwc-1/trunk}
				\\ \texttt{/ide/assignment}
		\end{itemize}
	\item Compile the sketch%; from appropriate directory run the command
		\begin{itemize}
			\item \texttt{pio run}
		\end{itemize}
	\item Upload the sketch to Arduino
		\begin{itemize}
			\item \texttt{pio -t nobuild -t upload}
		\end{itemize}
\end{enumerate}
\bigskip
We've successfully implemented XNOR logic in Arduino.
\end{document}
